Election 2024

### 2024-11-02 paper/paper.qmd
File Cleanup and Parquet impelmentation

#| echo: false
#| fig-cap: "Summary statistics of key sample variabls by state. Shows high sampl size and numeric grade among all polls of swing states."
# Load the data (replace with your CSV file path)
df = pd.read_csv('../data/02-analysis_data/merged_swing_state_data.csv')

>>>>

#| echo: false
#| fig-cap: "Summary statistics of key sample variabls by state. Shows high sampl size and numeric grade among all polls of swing states."

df = pd.read_parquet('../data/02-analysis_data/merged_swing_state_data.parquet')
